Mining Pre-Exposure Prophylaxis Trends in Social Media Data

### 2016-05-15 draft/draft.tex
fix typo

By picking out the most relevant tweets to PrEP, and also classifying tweets as positive or negative, we quickly identified a handful of specific tweets that highlight important parts of the online PrEP discussion. We identified two important arguments for and against PrEP. One, as explored by blog author Steven Banning hypothesizes that PrEP adoption could lead to unintended, and unhealthy risk seeking behavior. The contrary hypothesis, described by blog author Even Peterson, suggests that PrEP adoption is a product of healthy, responsible at-risk individuals who are gaining HIV protection in an effective form. These opposing arguments were identified automatically using large scale social media data. Further investigation and data analysis, of social media data, or other health data may be able to quantify PrEP and Truvada's effectiveness in the ongoing effort to prevent HIV infection.

>>>>

By picking out the most relevant tweets to PrEP, and also classifying tweets as positive or negative, we quickly identified a handful of specific tweets that highlight important parts of the online PrEP discussion. We identified two important arguments for and against PrEP. One, as explored by blog author Steven Banning hypothesizes that PrEP adoption could lead to unintended, and unhealthy risk seeking behavior. The contrary hypothesis, described by blog author Evan Peterson, suggests that PrEP adoption is a product of healthy, responsible at-risk individuals who are gaining HIV protection in an effective form. These opposing arguments were identified automatically using large scale social media data. Further investigation and data analysis, of social media data, or other health data may be able to quantify PrEP and Truvada's effectiveness in the ongoing effort to prevent HIV infection.
